%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}
 %-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
% Usage: \cvpublicationentry{<publisher>}{<title>}{<authors>}{<description>}{<date>}{<link>}
\begin{cventries}
 %---------------------------------------------------------
  
   \cvpublicationentry
   	{Cancers} % Publisher
    {The PI3K/mTOR pathway is targeted by rare germline variants in patients with both melanoma and renal cell carcinoma} % Title
    {Jean-Noël Hubert, Voreak Suybeng, Maxime Vallée, \textbf{Tiffany M Delhomme} \textit{et al.}} % Authors
    {}
    {May 2021} % Date(s)
    {https://www.mdpi.com/2072-6694/13/9/2243}
    
    \cvpublicationentry
   	{Int. J. Mol. Sci.} % Publisher
    {TP53 Targeted Deep Sequencing of Cell-Free DNA in Esophageal Squamous Cell Carcinoma Using Low-Quality Serum: Concordance with Tumor Mutation} % Title
    {Dariush Nasrollahzadeh, Gholamreza Roshandel, \textbf{Tiffany M Delhomme} \textit{et al.}} % Authors
    {}
    {May 2021} % Date(s)
    {https://www.mdpi.com/1422-0067/22/11/5627}
    
    \cvpublicationentry
   	{Cancers} % Publisher
    {The PI3K/mTOR Pathway Is Targeted by Rare Germline Variants in Patients with Both Melanoma and Renal Cell Carcinoma} % Title
    {Jean-Noël Hubert, Voreak Suybeng, Maxime Vallée, \textbf{Tiffany M Delhomme} \textit{et al.}} % Authors
    {}
    { 2021} % Date(s)
    {https://www.mdpi.com/2072-6694/13/9/2243}
    
    \cvpublicationentry
   	{Cancers} % Publisher
    {Development of sensitive droplet digital PCR assays for detecting urinary TERT promoter mutations as non-invasive biomarkers for detection of urothelial cancer} % Title
    {Ismail Hosen, Nathalie Forey, Geoffroy Durand, Catherine Voegele, Selin Bilici, Patrice H. Avogbe, \textbf{Tiffany M Delhomme} \textit{et al.}} % Authors
    {}
    {2020} % Date(s)
    {https://www.mdpi.com/2072-6694/12/12/3541}
    
    \cvpublicationentry
    {Nucleic Acid Res. - Genomics and Bioinformatics} % Publisher
    {needlestack: an ultra-sensitive variant caller for multi-sample deep next generation sequencing data} % Title
    {\textbf{Tiffany M.Delhomme}, Patrice H. Avogbe, Aurelie AA. Gabriel \textit{et al.}} % Authors
    {}
    {June 2020} % Date(s)
    {https://academic.oup.com/nargab/article/2/2/lqaa021/5822688}
    
    \cvpublicationentry
    {Nat. Commun.} % Publisher
    {Integrative and comparative genomic analyses identify clinically relevant groups of pulmonary carcinoids and unveil the existence of supra-carcinoids} % Title
    {Nicolas Alcala*, Noemie Leblay*, Aurelie Gabriel*, Lise Mangiante, David Hervas Marin, Theo Giffon, Anne-Sophie Sertier, Anthony Ferrari, Jules Derks, Akram Ghantous, \textbf{Tiffany M.Delhomme} \textit{et al.}} % Authors
    {}
    {Aug. 2019} % Date(s)
    {}

  \cvpublicationentry
    {EBioMedicine} % Publisher
    {Urinary TERT promoter mutations as non-invasive biomarkers for the comprehensive detection of urothelial cancer} % Title
    {Patrice H. Avogbe, Arnaud Manel, Emmanuel Vian, Geoffroy Durand, Nathalie Forey, Catherine Voegele, Maria Zvereva, Ismail Hosen, Sonia Meziani, Berengere De Tilly, Gilles Polo, Olesia Lole, Pauline Francois, \textbf{Tiffany M. Delhomme} \textit{et al.}} % Authors
    {}
    {June 2019} % Date(s)
    {https://www.sciencedirect.com/science/article/pii/S2352396419303056}

  \cvpublicationentry
    {Nature Communications} % Publisher
    {Integrative genomic profiling of large-cell neuroendocrine carcinomas reveals distinct subtypes of high-grade neuroendocrine lung tumors} % Title
    {Julie George, Vonn Walter, Martin Peifer, Ludmil B. Alexandrov, Danila Seidel, Frauke Leenders, Lukas Maas, Christian Müller, Ilona Dahmen, \textbf{Tiffany M.Delhomme} \textit{et al.}} % Authors
    {}
    {Mar. 2018} % Date(s)
    {https://www.nature.com/articles/s41467-018-03099-x}

  \cvpublicationentry
    {Oncotarget} % Publisher
    {KRAS mutations in blood circulating cell-free DNA: a pancreatic
cancer case-control study} % Title
    {Florence Le Calvez-Kelm, Matthieu Foll, Magdalena B. Wozniak, \textbf{Tiffany M.Delhomme} \textit{et al.}} % Authors
    {}
    {Oct. 2016} % Date(s)
    {https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5346680/pdf/oncotarget-07-78827.pdf}

 
  \cvpublicationentry
    {EBioMedicine} % Publisher
    {Identification of Circulating Tumor DNA for the Early Detection of Small-cell Lung Cancer} % Title
    {Lynnette Fernandez-Cuesta*, Sandra Perdomo*, Patrice H.Avogbe*, Noemie Leblay, \textbf{Tiffany M.Delhomme} \textit{et al.}} % Authors
    {Contribution: development of needlestack, an highly sensitive variant caller that can detect low abundance mutations such as tumor-derived mutations from circulating tumor DNA data. In this study, we applied needlestack to Small-cell Lung Cancer cases and matched controls in order to use circulating tumor DNA as an early cancer biomarker.}
    {Aug. 2016} % Date(s)
    {https://www.sciencedirect.com/science/article/pii/S2352396416302894}


 \cvsubsection{Submitted}
 
     \cvpublicationentry
    {} % Publisher
    {Disentangling heterogeneity of Malignant Pleural Mesothelioma through deep integrative omics analyses} % Title
    {Lise Mangiante*, Nicolas Alcala*, Alex Di Genova*, Alexandra Sexton-Oates*, [+14], \textbf{Tiffany M. Delhomme} \textit{et al.}} % Authors
    {}
    {Nat. Commun. 2022} % Date(s)
    {}     
    
 \cvsubsection{In preparation}

    \cvpublicationentry
    {} % Publisher
     {Proton and alpha radiation-induced mutational profiles in human cells} % Title
    {\textbf{Tiffany M. Delhomme}, Manuela Buonanno, Veljko Grilj, Josep Biayna, Fran Supek} % Authors
    {}
    {To be submitted in July 2022} % Date(s)
    {}

    \cvpublicationentry
    {} % Publisher
    {Assessment of the diagnostic value of circulating RB1 and
TP53 mutations for early detection of small cell lung cancers} % Title
    {Patrice H. Avogbe*, \textbf{Tiffany M.Delhomme}* \textit{et al.}} % Authors
    {}
    {expected sub. Dec. 2022} % Date(s)
    {}
    
\end{cventries}
